\LARGE \bf Autonomous Service Vehicle Development for Urban Road Navigation

### 2017-05-20 ieee-pandoc-template/paper.tex
mend

Recent advancements in robotics technology have brought great benefit to
autonomous vehicle research. Since the Defense Advanced Research
Projects Agency (DARPA) 2003 Grand Challenge
\citep{ventures2006stanley}, many research groups have focused their
effort to solving problems related to autonomous vehicle navigation. As
laboratories and research centers bringing the autonomous vehicle
technologies to real world applications \citep{Ford_Jan_16}, acceptance
of fully unmanned vehicles will still be a challenge. However, with
current progress it can be shown that for a specific problem domain, in
this case service vehicles, the autonomous vehicle can be utilized for
automation of human service oriented tasks, such as automated road
cleaning, grass cutting and leaves sucking machine. This is supported by
the growth of service robotics industry in the recent years
\citep{SVR_Nov_15}. \citeauthor{7225673} \citep{7225673} introduced
mobile service robot for electrical power plant inspection. This in turn
could reduce or replace human involvement in manual inspection process.
\citeauthor{6629559} \citep{6629559} presented an autonomous driving car
for research purposes that includes features that allows for urban road
navigation. Similarly, \citeauthor{7225765} \citep{7225765} introduced a
more advanced autonomous driving platform consisting of high performance
cameras, LIDARs, and other navigation sensors. While these platforms are
very attractive in term of their capability of handling big streams of
sensors data, the demanding computing power renders them unsuitable for
small service vehicle. The Autonomous Service Vehicle (ASV) proposed in
this paper is developed as a prototype to demonstrate autonomous vehicle
capability tasked for a service vehicle.

Autonomous platforms are usually retrofitted from manually driven
vehicles. This approach is commonly used because it is the most viable
and affordable way to install a Drive-By-Wire (DBW) system into existing
vehicle rather than to entirely build a new one. It was also studied
that automation driver's task has positive impact to improving driving
safety \citep{stanton1996fly}. Various effort to assist drivers has lead
to development of ADAS system \citep{6232125, 7225760}. A DBW enables
computerized control of the vehicle by means of replacing human drivers
with actuators, which are usually driven by electrical motors
\citep{1035218}. The ASV presented in this paper is retrofitted from a
compact electric vehicle \citep{SongZW_IV_2015}, and thus we studied the
feasibility of converting this class of vehicles into service vehicles.

@@

As opposed to indoor localization, the environment where ASV usually
deployed is outdoor and GPS data is available. However, it is studied
that GPS data is often contain errors that is too large for autonomous
navigation \citep{6629559}. One approach to compensate the error is to
use local lane marker or road boundary information to adjust lateral
position of the vehicle with respect to the road \citep{loc_Boss}. This
allow the vehicle control to always offset the vehicle position to
always stay on the drivable area on the road. However, it can be argued
that the position in longitudinal direction along the road with this
approach is not accurate. For service applications, it is necessary that
both lateral and longitudinal position of the vehicle are determined
accurately as the ASV often need to stop at specific point in its route.
We developed a hybrid approach that fuses both information from GPS and
a prior map based online localization. The method is based on Particle
Filter or sequential Bayes filter that involves prediction from vehicle
motion model and measurement update cycle \citep{6550131}. The
measurement update computed from GPS and the feature scan matching. This
approach is suitable for service applications because the size of the
map is ranging from small to medium scale up to a few kilometer squares.
With the current computing technology, the map of this size can be fully
loaded into memory.

@@

During operation of the ASV, obstacle obstructing or near the vehicle
should be considered. Thus, by using a laser range sensor model for
detection, a set \(L\) of \(n\) points which each has a range \(r_{i}\)
and a angle \(\alpha_{i}\), measured from laser beams
\(L=\left\{(r_{1},\alpha_{1}),...,(r_{n},\alpha_{n})\right\}\) are
clustered to extract objects \citep{Juric-Kavelj2008_407}. A Gaussian
smoothing is applied to remove spurious noise before processing. Two
subsequent points belong to one cluster satisfies the distance threshold
\(d(r_{i},r_{i+1}) \leq D_{0}+D_{1}min(r_{i},r_{i+1})\), where \(D_{0}\)
is the accuracy of the range data.
\(D_{1} = \frac{3}{2}(\alpha_{i+1}-\alpha_{i})\) is a constant that
determine maximum change allowed. Point that break the threshold will be
the start of another cluster. Processed laser scanner is represented by
a set of clusters \(\left\{ C_{1},...,C_{m} \right\}\). Each cluster
consists of tuples
\(({}^{C}r_{i},{}^{C}\alpha_{i},{}^{C}x_{i},{}^{C}y_{i})\) where
\({}^{C}x_{i}\), \({}^{C}y_{i}\) are the Cartesian coordinate
representations.

Each cluster is a potentially detected object. Based on the lateral
proximity of each cluster, object boundaries are found by determining if
each cluster satisfies \(w_{min} \leq d(y_{min},y_{max}) \leq w_{max}\),
where \(w_{max}\) and \(w_{min}\) depend on widths of object of
interest. The detected obstacles are sent the path planner to aid in
calculation of the navigation course. Moreover, obstacle detection
improves false recognition removal of map objects for localization
\citep{5164269}. The cluster points of detected objects are used to
determine areas of where measured points should be excluded from the
localization and mapping process.

@@

Global path planning aims to generate the waypoints to connect the
destination and the start point. In the literature, global path planning
can be achieved by the notable path planning algorithm such
\(A^{*}\)\citep{hart1968formal}, \(D^{*}\)\citep{stentz1994optimal},
Rapidly-Exploring Random Trees\citep{lavalle1998rapidly}, Probabilistic
roadmaps\citep{kavraki1996probabilistic}. For the ASV, a teach and
repeat solution is prefered as the planned path rarely change. This
implies that once the ASV is taught to navigate through certain
waypoints, it will be able to repeat it and more complex routing can be
achieved by combining multiple sets of waypoints. The ASV obtain its
trajectory by recording the vehicle position provided by localization
during manual driving. The trajectory obtained is further optimized by
post processing Alg. \ref{alg_global_waypoints}. In post processing
duplicate vehicle position points, points lie on straight line, curved
points within vehicle turning radius are removed to generate the
optimized path.

@@

Where \(GB\) is gas-brake position value, \(E\) is the velocity error,
\(dE\) is the differential error, \(k_p\) is the proportional gain,
\(k_i\) is the integral gain, \(k_d\) is the differential gain.

@@

Lateral control aims to control the steering angle of the vehicle based
on trajectory generated by path planner. The lateral controller is
developed based on Stanley's \citep{ventures2006stanley} steering
controller. Stanley steering controller is the geometric path tracking
approach used by Stanford university's autonomous vehicle during DARPA
grand challenge 2006. The closed-loop geometric tracking controller
helps vehicle to follow the desired path generated by local path
planning. The controller is based on non-linear cross track error
\(C_{e}\) and heading error \(\theta_{e}\). Cross track error is the
lateral distance between front axle center point \((P_{x}, P_{y})\) and
closest reference point \((R_{x}, R_{y})\) for which exponential can be
shown \citep{ventures2006stanley}. This term helps the vehicle to steer
towards the path to yield \(C_{e}\) as zero when its following the path.
The heading error \(\theta_{e}\) is calculated by difference in vehicle
heading \(\theta\) and reference heading \(\theta_{r}\) of path at
\((R_{x}, R_{y})\). This error term directly applies to steering angle
\(\delta\) with some steering angle limitation.

@@

When the cross track error \(C_{e}\) is non-zero, it adjusts \(\delta\)
such that the intended trajectory intersects the reference path tangent
from \((R_{x}, R_{y})\) at velocity in time \(V_{t}\) units from the
front axle center point \((P_{x}, P_{y})\). The resulting steering
control law by combining the two terms are shown in
(\ref{eqn_stanley_equation}). \(k_{h}\) and \(k_{c}\) are the gain
constants for heading error and cross error, respectively. Fig.
\ref{fig_stanley} illustrates the geometric relationship of control
parameters.

@@

The power supply for the CPU, DBW, sensors and other peripherals is
provided by a separated rechargeable Lithium Polymer (LiPo) batteries.
The autonomous operation runs independently on the LiPo batteries to
avoid complication that may arise if the main batteries is tapped.
Furthermore, power supply for ASV is crucial as the autonomous system
depends on it. Therefore, additional Power Supply Units (PSU) and a UPS
are installed such as shown in Fig. \ref{fig_power}. There are multiple
redundancies power line to secure fail-safe and fault-tolerant operation
of the ASV during its navigation. In addition, VI unit is made of
multiple stack of microcontroller and relay boards in order to ensure
safe interfacing to/from the vehicle. Fans are installed to provide
regulate temperature inside the box.

@@

Odometry position is estimated via accumulating the motion sensors data
over time. Pure odometry position is not recommended for long-term
navigation, since the motion sensor error will accumulate drift in the
actual position over time. The navigation relies on the localization
module to fuse odometry data with GPS data and the developed map based
localization. The odometry position is derived from the equation
\ref{eqn_simple_odometry}. The following two motion sensors are
installed in the ASV: a wheel motion sensor (Kistler Wheel Pulse
Transducers) to calculate vehicle travelled distance, and GPS/IMU sensor
(Xsens MTi-G-700 GPS) to measure global positions and heading rate.

@@

where \(\Delta\theta\) is the yaw rate obtained from IMU, \(\theta\) is
the heading, \(\Delta v\) is distance obtained from wheel motion sensor,
\(x\) and \(y\) are the Cartesian coordinates of the odometry position,
and \(t\) is the time index which is increased every sampling time.

@@

LIDAR ( Light Detection and Ranging) is one of the popular light range
sensors used in various field of Robotics, Autonomous Vehicles, and
Geo-mapping, forestry, etc. LIDAR will provide the distance of the
object by emitting laser towards it and analysing its reflection.
Compared to stereo vision systems \citep{6856563}, LIDARs generally has
more field of view, longer detection range, and more accurate depth
information. A four layers Lidar (Ibeo ScaLa) is mounted on front bumper
facing forward for obstacle detection up to 100 meters. The obstacle
detection can be done in one layer, but the other layers will provide
redundancies if the ASV tilt forward or backward. In this case, one or
more layers can hit the ground or the free space below or above an
object, respectively. At least one layer will detect an object if there
is one. Another 16 layers Lidar (Velodyne Puck) which can sense
surrounding object and environment shape in 25m radius is used mainly
for localization. This LIDAR is mounted roughly \(30^{\circ}\) towards
ground purposely for detecting main features of the environment such as
the road curbs and the tree trunks which are used for localization.

@@

Depending on the specific task, various tools which include sensors
and/or actuators that are necessary for the service task can be mounted
onto the ASV. These sensors and actuators are collectively called as a
workload. The ASV modules are customizable to carry the workload and
perform the desired service task. The ASV localize itself by using
information from map and GPS, thus eliminating the need for installing
environmental guidance such as RFID \citep{7225673} or magnetic rails
\citep{5354591}. For inspection and surveillance purposes, the camera
data can be streamed and recorded via the HMI. For cleaning service, the
ASV perform its task during its movement. This necessitates that the
path planning follows certain objects, such as road pavement or curb.
Combined with the method proposed in \citep{SongZW_IV_2015}, the ASV can
navigate to track arbitrary distinguishable object boundaries to conduct
the cleaning. Nevertheless, thanks to the developed localization,
arbitrary path rerouting is also possible. For services that require
following certain moving object such as pedestrian \citep{7139259}, the
LIDAR and camera sensors could be used to track the object.
Subsequently, the tracked object positions will become the destination
points for the ASV path planner.

@@

\section*{Acknowledgments}\label{acknowledgments}
\addcontentsline{toc}{section}{Acknowledgments}

Thanks the Autonomous Vehicle Department in Institute for Infocomm
Research for the accomplishment of successful demonstrations within a
short development time. The conception of human service applications
stemmed from this endeavor has lead to the publication of this paper.
The project was supported by the Exploit Technologies Private Limited
(ETPL) of the Agency for Science, Technology and Research (A*STAR) of
Singapore.

>>>>

Recent advancements in robotics technology have brought great benefit to
autonomous vehicle research. Since the Defense Advanced Research
Projects Agency (DARPA) 2003 Grand Challenge
\citep{ventures2006stanley}, many research groups have focused their
effort to solving problems related to autonomous vehicle navigation. As
laboratories and research centers bringing the autonomous vehicle
technologies to real world applications \citep{Ford_Jan_16}, acceptance
of fully unmanned vehicles will still be a challenge. However, with
current progress it can be shown that for a specific problem domain, in
this case service vehicles, the autonomous vehicle can be utilized for
automation of human service oriented tasks, such as automated road
cleaning, grass cutting and leaves sucking machine. This is supported by
the growth of service robotics industry in the recent years
\citep{SVR_Nov_15}. \citeauthor{7225673} {[}@7225673{]} introduced
mobile service robot for electrical power plant inspection. This in turn
could reduce or replace human involvement in manual inspection process.
\citeauthor{6629559} {[}@6629559{]} presented an autonomous driving car
for research purposes that includes features that allows for urban road
navigation. Similarly, \citeauthor{7225765} {[}@7225765{]} introduced a
more advanced autonomous driving platform consisting of high performance
cameras, LIDARs, and other navigation sensors. While these platforms are
very attractive in term of their capability of handling big streams of
sensors data, the demanding computing power renders them unsuitable for
small service vehicle. The Autonomous Service Vehicle (ASV) proposed in
this paper is developed as a prototype to demonstrate autonomous vehicle
capability tasked for a service vehicle.

Autonomous platforms are usually retrofitted from manually driven
vehicles. This approach is commonly used because it is the most viable
and affordable way to install a Drive-By-Wire (DBW) system into existing
vehicle rather than to entirely build a new one. It was also studied
that automation driver's task has positive impact to improving driving
safety \citep{stanton1996fly}. Various effort to assist drivers has lead
to development of ADAS system {[}@6232125;@7225760{]}. A DBW enables
computerized control of the vehicle by means of replacing human drivers
with actuators, which are usually driven by electrical motors
{[}@1035218{]}. The ASV presented in this paper is retrofitted from a
compact electric vehicle \citep{SongZW_IV_2015}, and thus we studied the
feasibility of converting this class of vehicles into service vehicles.

@@

As opposed to indoor localization, the environment where ASV usually
deployed is outdoor and GPS data is available. However, it is studied
that GPS data is often contain errors that is too large for autonomous
navigation {[}@6629559{]}. One approach to compensate the error is to
use local lane marker or road boundary information to adjust lateral
position of the vehicle with respect to the road \citep{loc_Boss}. This
allow the vehicle control to always offset the vehicle position to
always stay on the drivable area on the road. However, it can be argued
that the position in longitudinal direction along the road with this
approach is not accurate. For service applications, it is necessary that
both lateral and longitudinal position of the vehicle are determined
accurately as the ASV often need to stop at specific point in its route.
We developed a hybrid approach that fuses both information from GPS and
a prior map based online localization. The method is based on Particle
Filter or sequential Bayes filter that involves prediction from vehicle
motion model and measurement update cycle {[}@6550131{]}. The
measurement update computed from GPS and the feature scan matching. This
approach is suitable for service applications because the size of the
map is ranging from small to medium scale up to a few kilometer squares.
With the current computing technology, the map of this size can be fully
loaded into memory.

@@

During operation of the ASV, obstacle obstructing or near the vehicle
should be considered. Thus, by using a laser range sensor model for
detection, a set $L$ of $n$ points which each has a range $r_{i}$ and a
angle $\alpha_{i}$, measured from laser beams
$L=\left\{(r_{1},\alpha_{1}),...,(r_{n},\alpha_{n})\right\}$ are
clustered to extract objects \citep{Juric-Kavelj2008_407}. A Gaussian
smoothing is applied to remove spurious noise before processing. Two
subsequent points belong to one cluster satisfies the distance threshold
$d(r_{i},r_{i+1}) \leq D_{0}+D_{1}min(r_{i},r_{i+1})$, where $D_{0}$ is
the accuracy of the range data.
$D_{1} = \frac{3}{2}(\alpha_{i+1}-\alpha_{i})$ is a constant that
determine maximum change allowed. Point that break the threshold will be
the start of another cluster. Processed laser scanner is represented by
a set of clusters $\left\{ C_{1},...,C_{m} \right\}$. Each cluster
consists of tuples
$({}^{C}r_{i},{}^{C}\alpha_{i},{}^{C}x_{i},{}^{C}y_{i})$ where
${}^{C}x_{i}$, ${}^{C}y_{i}$ are the Cartesian coordinate
representations.

Each cluster is a potentially detected object. Based on the lateral
proximity of each cluster, object boundaries are found by determining if
each cluster satisfies $w_{min} \leq d(y_{min},y_{max})  \leq w_{max}$,
where $w_{max}$ and $w_{min}$ depend on widths of object of interest.
The detected obstacles are sent the path planner to aid in calculation
of the navigation course. Moreover, obstacle detection improves false
recognition removal of map objects for localization {[}@5164269{]}. The
cluster points of detected objects are used to determine areas of where
measured points should be excluded from the localization and mapping
process.

@@

Global path planning aims to generate the waypoints to connect the
destination and the start point. In the literature, global path planning
can be achieved by the notable path planning algorithm such
$A^{*}$\citep{hart1968formal}, $D^{*}$\citep{stentz1994optimal},
Rapidly-Exploring Random Trees\citep{lavalle1998rapidly}, Probabilistic
roadmaps\citep{kavraki1996probabilistic}. For the ASV, a teach and
repeat solution is prefered as the planned path rarely change. This
implies that once the ASV is taught to navigate through certain
waypoints, it will be able to repeat it and more complex routing can be
achieved by combining multiple sets of waypoints. The ASV obtain its
trajectory by recording the vehicle position provided by localization
during manual driving. The trajectory obtained is further optimized by
post processing Alg. \ref{alg_global_waypoints}. In post processing
duplicate vehicle position points, points lie on straight line, curved
points within vehicle turning radius are removed to generate the
optimized path.

@@

Where $GB$ is gas-brake position value, $E$ is the velocity error, $dE$
is the differential error, $k_p$ is the proportional gain, $k_i$ is the
integral gain, $k_d$ is the differential gain.

@@

Lateral control aims to control the steering angle of the vehicle based
on trajectory generated by path planner. The lateral controller is
developed based on Stanley's \citep{ventures2006stanley} steering
controller. Stanley steering controller is the geometric path tracking
approach used by Stanford university's autonomous vehicle during DARPA
grand challenge 2006. The closed-loop geometric tracking controller
helps vehicle to follow the desired path generated by local path
planning. The controller is based on non-linear cross track error
$C_{e}$ and heading error $\theta_{e}$. Cross track error is the lateral
distance between front axle center point $(P_{x}, P_{y})$ and closest
reference point $(R_{x}, R_{y})$ for which exponential can be shown
\citep{ventures2006stanley}. This term helps the vehicle to steer
towards the path to yield $C_{e}$ as zero when its following the path.
The heading error $\theta_{e}$ is calculated by difference in vehicle
heading $\theta$ and reference heading $\theta_{r}$ of path at
$(R_{x}, R_{y})$. This error term directly applies to steering angle
$\delta$ with some steering angle limitation.

@@

When the cross track error $C_{e}$ is non-zero, it adjusts $\delta$ such
that the intended trajectory intersects the reference path tangent from
$(R_{x}, R_{y})$ at velocity in time $V_{t}$ units from the front axle
center point $(P_{x}, P_{y})$. The resulting steering control law by
combining the two terms are shown in (\ref{eqn_stanley_equation}).
$k_{h}$ and $k_{c}$ are the gain constants for heading error and cross
error, respectively. Fig. \ref{fig_stanley} illustrates the geometric
relationship of control parameters.

@@

The power supply for the CPU, DBW, sensors and other peripherals is
provided by a separated rechargeable Lithium Polymer (LiPo) batteries.
The autonomous operation runs independently on the LiPo batteries to
avoid complication that may arise if the main batteries is tapped.
Furthermore, power supply for ASV is crucial as the autonomous system
depends on it. Therefore, additional Power Supply Units (PSU) and a UPS
are installed such as shown in Fig. \ref{fig_power}. There are multiple
redundancies power line to secure fail-safe and fault-tolerant operation
of the ASV during its navigation. In addition, VI unit is made of
multiple stack of microcontroller and relay boards in order to ensure
safe interfacing to/from the vehicle. Fans are installed to regulate
temperature inside the box.

@@

Odometry position is estimated via accumulating the motion sensors data
over time. Pure odometry position is not recommended for long-term
navigation, since the motion sensor error will accumulate drift in the
actual position over time. The navigation relies on the localization
module to fuse odometry data with GPS data and the developed map based
localization. The odometry position is derived from the
(\ref{eqn_simple_odometry}). The following two motion sensors are
installed in the ASV: a wheel motion sensor (Kistler Wheel Pulse
Transducers) to calculate vehicle travelled distance, and GPS/IMU sensor
(Xsens MTi-G-700 GPS) to measure global positions and heading rate.

@@

where $\Delta\theta$ is the yaw rate obtained from IMU, $\theta$ is the
heading, $\Delta v$ is distance obtained from wheel motion sensor, $x$
and $y$ are the Cartesian coordinates of the odometry position, and $t$
is the time index which is increased every sampling time.

@@

LIDAR ( Light Detection and Ranging) is one of the popular light range
sensors used in various field of Robotics, Autonomous Vehicles, and
Geo-mapping, forestry, etc. LIDAR will provide the distance of the
object by emitting laser towards it and analysing its reflection.
Compared to stereo vision systems {[}@6856563{]}, LIDARs generally has
more field of view, longer detection range, and more accurate depth
information. A four layers Lidar (Ibeo ScaLa) is mounted on front bumper
facing forward for obstacle detection up to 100 meters. The obstacle
detection can be done in one layer, but the other layers will provide
redundancies if the ASV tilt forward or backward. In this case, one or
more layers can hit the ground or the free space below or above an
object, respectively. At least one layer will detect an object if there
is one. Another 16 layers Lidar (Velodyne Puck) which can sense
surrounding object and environment shape in 25m radius is used mainly
for localization. This LIDAR is mounted roughly $30^{\circ}$ towards
ground purposely for detecting main features of the environment such as
the road curbs and the tree trunks which are used for localization.

@@

Depending on the specific task, various tools which include sensors
and/or actuators that are necessary for the service task can be mounted
onto the ASV. These sensors and actuators are collectively called as a
workload. The ASV modules are customizable to carry the workload and
perform the desired service task. The ASV localize itself by using
information from map and GPS, thus eliminating the need for installing
environmental guidance such as RFID {[}@7225673{]} or magnetic rails
{[}@5354591{]}. For inspection and surveillance purposes, the camera
data can be streamed and recorded via the HMI. For cleaning service, the
ASV perform its task during its movement. This necessitates that the
path planning follows certain objects, such as road pavement or curb.
Combined with the method proposed in \citep{SongZW_IV_2015}, the ASV can
navigate to track arbitrary distinguishable object boundaries to conduct
the cleaning. Nevertheless, thanks to the developed localization,
arbitrary path rerouting is also possible. For services that require
following certain moving object such as pedestrian {[}@7139259{]}, the
LIDAR and camera sensors could be used to track the object.
Subsequently, the tracked object positions will become the destination
points for the ASV path planner.

@@
